%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Systems Engineer II} % Job title
{Fred Hutchinson Cancer Research Center} % Organization
{Seattle, WA} % Location
{Apr. 2018 - Current} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Currently rearchitecting cross-platform public cloud environments; this includes tools used, logical account management, user management, child account provisioning, and infrastructure automation.}
\item {Working towards containerizing legacy applications and offering Docker container consulting, design, and hosting as a managed Kubernetes service to staff.}
\item {Designed and implemented a custom ElasticSearch-based search engine leveraging open source technologies and multiple unique data sources.}
\item {Deployed Atlassian Jira, Confluence, and Crowd for SSO enabled cross-department productivity and documentation. Built workflows for teams to consolidate multiple issue-tracking platforms into one. }
\item {Implemented Terraform, Packer, and Vault to automate secure infrastructure deployment and created training curriculum to evangelize new tooling. Modified existing open-source Terraform plugins to work with on-premises appliances. Extended functionality of these tools with creative Bash and Python scripts.}
\item {Overhauled Chef recipes to more closely align with Linux best practices. Currently converting configuration management to Ansible playbooks and developing a CI process for deployment.}
\item {Implemented GitLab to consolidate the Fred Hutch SCM/CI/CD strategy. Developed pipelines to allow data scientists and engineers to work with public cloud resources.}
\item {Consolidated Linux machine management on FreeIPA to handle user authentication, SSH key management, and PKI. Federated with Active Directory domain and trusting the certificate authorities. }
\item {Assisted with backend architectural efforts in major website redesign, from AWS resource management to developer troubleshooting.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Network / Systems Engineer II} % Job title
{Amplero Inc.} % Organization
{Seattle, WA} % Location
{Feb. 2016 - Mar. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and implemented new AWS accounts, and facilitated cloud migration from VMWare to AWS infrastructure.}
\item {Conducted migration from parent company's VMware environment to AWS, as well as splitting out other services such as Active Directory into FreeIPA, migrating Confluence and Jira, and migrating Exchange 2010 to Office 365.}
\item {Managed a virtualized CentOS Linux environment with Windows machines to support Windows end-systems. Leveraged Puppet for all system configurations to maintain uniformity and version control, with Group Policy for Windows servers.}
\item {Operated and deployed a large range of 'big data' services across production networks, such as Cloudera Hadoop with Impala, HDFS, YARN, and Zookeeper. Other notable back end services include PostgreSQL and Apache.}
\item {Provided operational T3 24/7 on-call support to internal teams working with customers around the world, working directly with customers on data integration efforts and coordinating data center resources.}
\item {Responsible for providing primary IT support to a team of 45, as well as developing a training program for junior engineers.}\
\item {Promoted internally from Systems Engineer I.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Systems Engineer} % Job title
{Globys Inc.} % Organization
{Seattle, WA} % Location
{Feb. 2014 - Feb. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managed primarily Windows 2008 and 2012 Servers, with a minimal CentOS Linux population. Configuration mostly managed by Group Policy.}
\item {Conducted minor penetration testing against internal and external hosts utilizing Metasploit and other open source tooling. Assisted in drafting and implementing recommended security fixes, and bringing infrastructure up to PCI compliance.}
\item {Managed and deployed multiple VMware ESXi hosts, configuring for High Availability via vMotion.}
\item {Serviced and deployed Dell servers for a variety of purposes. Gained familiarity with internal components and troubleshooting steps.}
\item {Implemented custom Syslinux/Windows Deployment Services to provide on-the-fly machine deployment in both Windows and Linux.}
\item {Provided continual support for company websites in both code optimization and content deployment. Made significant improvements on Drupal platform to reduce latency and increase security.}
\item {Established Corporate IT knowledgebase for documentation centralization. Implemented Lansweeper for asset tracking and to fulfill CMDB requirements for PCI.}
\item {Promoted internally from IT Support Technician.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{On-Site Technician} % Job title
{Staples} % Organization
{Silverdale, WA} % Location
{Mar. 2012 - Jun. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managed customer appointments for home \& business repair. Serviced consumer and small-business computer systems on-site.}
\item {Leveraged Linux-based live distributions to accelerate work flow.}
\item {Promoted from Easy Tech Bench Technician.}
\end{cvitems}
}

%------------------------------------------------


\end{cventries}
